Reduced diversity and increased specialization of Alaska salmon fishermen:

### 2016-10-08 salmon/paper/salmon_paper.Rmd
paper

Figure 3: One component of variability is the year-to-year variation that individuals experience as a result of external forces (stock abundance, prices, etc). Or common fluctuations in revenue experienced by all permit holders [@anderson_benefits]. This shows the time varying intercepts on the mean -- negative equals losing revenue, positive = increasing revenue. This shows big differences between permit types (gillnets tend to have lower year-to-year variation). Some permits have extreme variation - S01E (PWS seine) has fluctuations between exp(-1) and exp(+1), corresponding to year-to-year changes of 36-270%.  
Figure 4 shows the time varying nature of of the model for all permits. These are the time series of benefits of changing from effective species diversity of 1 to 2, and here we're basically isolating year-to-year differences in revenue (the intercepts) from diversification benefits. In some cases the effect is positive (fishing more spp = more revenue). But in many cases it's not, and the trend is negative (indicating that specialization is more profitable over time). In several cases, these time series mirror the aggregate diversity in the raw time series (Fig. 1).

>>>>

Figure 3: One component of variability is the year-to-year variation that individuals experience as a result of external forces (stock abundance, prices, etc). Or common fluctuations in revenue experienced by all permit holders [@anderson_benefits]. This shows the time varying intercepts on the mean -- negative equals losing revenue on average, positive = increasing revenue. This shows big differences between permit types (gillnets tend to have lower year-to-year variation). Some permits have extreme variation - S01E (PWS seine) has fluctuations between exp(-1) and exp(+1), corresponding to year-to-year changes of 36-270%.

Figure 4 shows the time varying nature of of the model for all permits. These are the time series of benefits of changing from effective species diversity of 1 to 2, and here we're basically isolating year-to-year differences in revenue (the intercepts) from diversification benefits. In some cases the effect is positive (fishing more spp = more revenue). But in many cases it's not, and the trend is negative (indicating that specialization is more profitable over time). In some cases, these time series mirror the aggregate diversity in the raw time series (Fig. 1). I think we also expect this result - fishermen increase diversity or not, because it's profitable.
